Constrained ordination method as a tool for performing genome scan and environmental genomic studies

### 2017-01-30 article_genome_scan.tex
Add files via upload

Redundancy analysis (RDA) was first introduced by \citep{Rao1964} and is clearly described in \citep{LegendrePierre&Legendre2013} section 11.1. It is the direct extension of multiple regression to the modeling of multivariate response data. Typically the data to be analysed are separated in two sets, a response matrix Y of variable to be explained (e.g. species abundance in a set of sites; m sites and n species) and an explanatory matrix X (e.g.  a set of environmental variable within each site; m sites and p environment). 
	In the following analysis, species are replaced by loci and sites by individuals. In other word, we wish to project on a reduced space the proportion of variance in genetic difference between individuals which is better explained by environmental data.
	After this ordination, we follow the \citet{Luu2016} methodology to compute pvalues. First we compute the test statistic by regressing each of the p SNPs by the K ordination axis $X_1, ..., X_K$.

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[height=0.4\textheight]{figures/overallresults.eps}
\end{center}
\caption{Performance results of rda and pcadapt methods. Each performance value is averaged over 100 simulated dataset (error bars are displayed but hardly visible since they are very scarce). fdr, is the false discovery rate. power is given for the whole selected loci and seperately for loci coding for quantitative trait 1, 2 and 3.}%
\label{fig:performance}%
\end{figure*}

@@

Results summarized on Fig \ref{fig:performance} is confirming that both methods have a good control of false discovery rate ($\approx 0.1$) and that overall RDA shows better performance at detecting true outliers since it succeeds to detect quite often QTL1 and QTL3 SNPs. It seems however less efficient at detecting QTL3 outliers but this might be due to the fact that local adaptation on a coarse environment is more difficult  that adaptation on a smooth environmental gradient as environment 1 and 2. These simulations plead in favor of using constrained ordination method instead of PCA when non genetic data such as environmental variable are available in order to orientate the axis in the direction of informative gradients.

>>>>

Redundancy analysis (RDA) was first introduced by \citep{Rao1964} and is clearly described in \citep{Legendre2012} section 11.1. It is the direct extension of multiple regression to the modeling of multivariate response data. Typically the data to be analysed are separated in two sets, a response matrix Y of variable to be explained (e.g. species abundance in a set of sites; m sites and n species) and an explanatory matrix X (e.g.  a set of environmental variable within each site; m sites and p environment). 
	In the following analysis, species are replaced by loci and sites by individuals. In other word, we wish to project on a reduced space the proportion of variance in genetic difference between individuals which is better explained by environmental data.
	After this ordination, we follow the \citet{Luu2016} methodology to compute pvalues. First we compute the test statistic by regressing each of the p SNPs by the K ordination axis $X_1, ..., X_K$.

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[height=0.4\textheight]{figures/overallresults.eps}
\end{center}
\caption{Performance results of rda and pcadapt methods. Each performance value is averaged over 100 simulated dataset (error bars are displayed but hardly visible since they are very scarce). Power is given seperately for loci coding for quantitative trait 1, 2 and 3.}%
\label{fig:performance}%
\end{figure*}

@@

Results summarized on Fig \ref{fig:performance} is confirming that both methods have a good control of false discovery rate ($8.36 \times 10^{-2}$ for pcadapt and $8.51 \times 10^{-2}$ for RDA) and that overall RDA shows better performance at detecting true outliers since it succeeds to detect quite often QTL1 and QTL3 SNPs. It seems however less efficient at detecting QTL3 outliers but this might be due to the fact that local adaptation on a coarse environment is more difficult  that adaptation on a smooth environmental gradient as environment 1 and 2. These simulations plead in favor of using constrained ordination method instead of PCA when non genetic data such as environmental variable are available in order to orientate the axis in the direction of informative gradients.
